### 2017-06-22 categorical-models.tex
categorical-models

\begin{definition}
\label{def:mc}
  A \textbf{monoidal category} $(\cat{M},\otimes,I,\alpha,\lambda,\rho)$ is a category $\cat{M}$
  consists of
  \begin{itemize}
  \item a bifunctor $\otimes:\cat{M}\times\cat{M}\rightarrow\cat{M}$, called the tensor product;
  \item an object $I$, called the unit object;
  \item three natural isomorphisms $\alpha$, $\lambda$, and $\rho$ with components
        $$\alpha_{A,B,C}:(A\otimes B)\otimes C\rightarrow A\otimes(B\otimes C)$$
        $$\lambda_A:I\otimes A\rightarrow A$$
        $$\rho_A:A\otimes I\rightarrow A$$
        where $\alpha$ is called associator, $\lambda$ is left unitor, and $\rho$ is right
        unitor,
  \end{itemize}
  such that the following diagrams commute for any objects $A$, $B$, $C$ in $\cat{M}$:
  \begin{mathpar}
  \bfig
    \square/`->`->`->/<2100,400>[
      ((A\otimes B)\otimes C)\otimes D`
      A\otimes((B\otimes C)\otimes D)`
      (A\otimes B)\otimes(C\otimes D)`
      A\otimes(B\otimes(C\otimes D));
      `
      \alpha_{A\otimes B,C,D}`
      id_A\otimes\alpha_{B,C,D}`
      \alpha_{A,B,C\otimes D}]
    \morphism(0,400)<1100,0>[
      ((A\otimes B)\otimes C)\otimes D`
      (A\otimes(B\otimes C))\otimes D;
      \alpha_{A,B,C}\otimes id_D]
    \morphism(1100,400)<1000,0>[
      (A\otimes(B\otimes C))\otimes D`
      A\otimes((B\otimes C)\otimes D);
      \alpha_{A,B\otimes C,D}]
  \efig
  \and
  \bfig
    \Vtriangle<400,400>[
      (A\otimes I)\otimes B`
      A\otimes(I\otimes B)`
      A\otimes B;
      \alpha_{A,I,B}`
      \rho_A\otimes id_B`
      id_A\otimes\lambda_B]
  \efig
  \end{mathpar}
\end{definition}

\begin{definition}
  A \textbf{Lambek category} (or a \textbf{biclosed monoidal category}) is a monoidal category
  $(\cat{M},\otimes,I,\alpha,\lambda,\rho)$ equipped with two bifunctors
  $\rightharpoonup:\cat{M}^{op}\times\cat{M}\rightarrow\cat{M}$ and
  $\leftharpoonup:\cat{M}\times\cat{M}^{op}\rightarrow\cat{M}$ that are both right adjoint to
  the tensor product. That is, the following natural bijections hold:
  \begin{center}
  \begin{math}
  \begin{array}{lll}
    \Hom{L}{X\otimes A}{B}\cong\Hom{L}{X}{A\lto B} & \quad\quad\quad\quad & 
    \Hom{L}{A\otimes X}{B}\cong\Hom{L}{X}{B\rto A}
  \end{array}
  \end{math}
  \end{center}
\end{definition}

\begin{definition}
  A \textbf{symmetric monoidal category} is a monoidal category
  $(\cat{M},\otimes,I,\alpha,\lambda,\rho)$ together with a natural transformation with
  components $\e{A,B}:A\otimes B\rightarrow B\otimes A$, called exchange, such that the
  following diagrams commute:
  \begin{mathpar}
  \bfig
    \Vtriangle<300,400>[A\otimes I`I\otimes A`A;\e{A,I}`\rho_A`\lambda_A]
  \efig
  \and
  \bfig
    \Vtriangle/=`->`<-/<300,400>[
      A\otimes B`A\otimes B`B\otimes A;
      id_{A\otimes B}`\e{A,B}`\e{B,A}]
  \efig
  \and
  \bfig
    \hSquares/->`->`->``->`->`->/<400>[
      (A\otimes B)\otimes C`A\otimes(B\otimes C)`(B\otimes C)\otimes A`
      (B\otimes A)\otimes C`B\otimes(A\otimes C)`B\otimes(C\otimes A);
      \alpha_{A,B,C}`\e{A,B\otimes C}`\e{A,B}\otimes id_C``
      \alpha_{B,A,C}`\alpha_{B,A,C}`id_B\otimes\e{A,C}]
  \efig
  \end{mathpar}
\end{definition}

\begin{definition}
  A \textbf{symmetric monoidal closed category} $(\cat{M},\otimes,I,\alpha,\lambda,\rho)$ is a
  symmetric monoidal category equipped with a bifunctor
  $\limp:\cat{M}^{op}\times\cat{M}\rightarrow\cat{M}$ that is right adjoint to the tensor
  product. That is, the following natural bijection
  $\Hom{\cat{M}}{X\otimes A}{B}\cong\Hom{\cat{M}}{X}{A\limp B}$ holds.
\end{definition}

\begin{lemma}
  \label{lemma:internal-homs-collapse}
  Let $A$ and $B$ be two objects in a Lambek category with the exchange natural transformation.
  Then $(A \lto B) \cong (B \rto A)$.
\end{lemma}
\begin{proof}
  First, notice that for any object $C$ we have
  \begin{center}
  \begin{math}
  \small
  \begin{array}{lllll}
    Hom[C,A\lto B]
    & \cong & Hom[C\otimes A,B] & \cat{L}\text{ is a Lambek category}\\
    & \cong & Hom[A\otimes C,B] & \text{By the exchange }\e{C,A}\\
    & \cong & Hom[C,B\rto A]    & \cat{L}\text{ is a Lambek category}
  \end{array}
  \end{math}
  \end{center}  
  Thus, $A\lto B\cong B\rto A$ by the Yoneda lemma.
\end{proof}
\begin{corollary}
  \label{corollary:LC-with-ex-mc}
  A Lambek category with exchange is symmetric monoidal closed.
\end{corollary}

\begin{definition}
  Let $(\cat{M},\otimes,I,\alpha,\lambda,\rho)$ and
  $(\cat{M'},\otimes',I',\alpha',\lambda',\rho')$ be monoidal categories. A \textbf{monoidal
  functor} $(F,\m{})$ from $\cat{M}$ to $\cat{M'}$ is a functor $F:\cat{M}\rightarrow\cat{M'}$
  together with a morphism $\m{I}:I'\rightarrow F(I)$ and a natural transformation
  $\m{A,B}:FA'\otimes FB'\rightarrow F(A\otimes B)$, such that the following diagrams commute
  for any objects $A$, $B$, and $C$ in $\cat{M}$:
  \begin{mathpar}
  \bfig
    \hSquares/->`->`->``->`->`->/<400>[
      (FA\otimes'FB)\otimes'FC`FA\otimes'(FB\otimes'FC)`FA\otimes'F(B\otimes C)`
      F(A\otimes B)\otimes'FC`F((A\otimes B)\otimes C)`F(A\otimes(B\otimes C));
      \alpha'_{FA,FB,FC}`id_{FA}\otimes'\m{A,B}`\m{A,B}\otimes'id_{FC}``
      \m{A,B\otimes C}`\m{A\otimes B,C}`F\alpha_{A,B,C}]
  \efig
  \and
  \bfig
    \square/->`->`<-`->/<600,400>[
      I'\otimes'FA`FA`FI\otimes'FA`F(I\otimes A);
      \lambda'_{FA}`\m{I}\otimes id_{FA}`F\lambda_A`\m{I,A}]
  \efig
  \and
  \bfig
    \square/->`->`<-`->/<600,400>[
      FA\otimes'I'`FA`FA\otimes'FI`F(A\otimes I);
      \rho'_{FA}`\id_{FA}\otimes\m{I}`F\rho_A`\m{A,I}]
  \efig
  \end{mathpar}
\end{definition}

\begin{definition}
  Let $(\cat{M},\otimes,I,\alpha,\lambda,\rho)$ and
  $(\cat{M'},\otimes',I',\alpha',\lambda',\rho')$ be monoidal categories. A \textbf{symmetric
  monoidal functor} $F:\cat{M}\rightarrow\cat{M'}$ is a monoidal functor $(F,m)$ that satisfies
  the following coherence diagram:
  \begin{mathpar}
  \bfig
    \square<700,400>[
      FA\otimes'FB`FB\otimes'FA`F(A\otimes B)`F(B\otimes A);
      \e{FA,FB}`\m{A,B}`\m{B,A}`F\e{A,B}]
  \efig
  \end{mathpar}
\end{definition}

\begin{definition}
  An \textbf{adjunction} between categories $\cat{C}$ and $\cat{D}$ consists of two functors
  $F:\cat{D}\rightarrow\cat{C}$, called the \textbf{left adjoint}, and
  $G:\cat{C}\rightarrow\cat{D}$, called the \textbf{right adjoint}, and two natural
  transformations $\eta:id_\cat{D}\rightarrow GF$, called the \textbf{unit}, and
  $\varepsilon:FG\rightarrow id_\cat{C}$, called the \textbf{counit}, such that the following
  diagrams commute for any object $A$ in $\cat{C}$ and $B$ in $\cat{D}$:
  \begin{mathpar}
  \bfig
    \Vtriangle/->`=`->/<400,400>[FB`FGFB`FB;F\eta_B``\varepsilon_{FB}]
  \efig
  \and
  \bfig
    \Vtriangle/->`=`->/<400,400>[GA`GFGA`GA;\eta_{GA}``G\varepsilon_A]
  \efig
  \end{mathpar}
\end{definition}

\begin{definition}
  Let $(F,\m{})$ and $(G,\n{})$ be monoidal functors from a monoidal category $\cat{M}$ to a
  monoidal category $\cat{M'}$. A \textbf{monoidal natural transformation} from $(F,\m{})$ to 
  $(G,\n{})$ is a natural transformation $\theta:(F,\m{})\rightarrow(G,\n{})$ such that the
  following diagrams commute for any objects $A$ and $B$ in $\cat{M}$:
  \begin{mathpar}
  \bfig
    \square<700,400>[
      FA\otimes'FB`F(A\otimes B)`GA\otimes'GB`G(A\otimes B);
      \m{A,B}`\theta_A\otimes'\theta_B`\theta_{A\otimes B}`\n{A,B}]
  \efig
  \and
  \bfig
    \Vtriangle/->`<-`<-/<400,400>[FI`GI`I';\theta_I`\m{I}`\n{I}]
  \efig
  \end{mathpar}
\end{definition}

\begin{definition}
  Let $(\cat{M},\otimes,I,\alpha,\lambda,\rho)$ and
  $(\cat{M'},\otimes',I',\alpha',\lambda',\rho')$ be monoidal categories,
  $F:\cat{M}\rightarrow\cat{M'}$ and $G:\cat{M}'\rightarrow\cat{M}$ be functors. The adjunction
  $F:\cat{M}\dashv\cat{M'}:G$ is a \textbf{monoidal adjunction} if $F$ and $G$ are monoidal
  functors, and the unit $\eta$ and the counit $\varepsilon$ are monoidal natural
  transformations.
\end{definition}

@@

\begin{definition}
  Let $\cat{C}$ be a category. A \textbf{monad} on $\cat{C}$ consists of an endofunctor
  $T:\cat{C}\rightarrow\cat{C}$ together with two natural transformations
  $\eta:id_\cat{C}\rightarrow T$ and $\mu:T^2\rightarrow id_\cat{C}$, where $id_\cat{C}$
  is the identity functor on $\cat{C}$, such that the following diagrams commute:
  \begin{mathpar}
  \bfig
    \square<400,400>[T^3`T^2`T^2`T;T\mu`\mu_T`\mu`\mu]
  \efig
  \and
  \bfig
    \square<400,400>[T`T^2`T^2`T;\eta_T`T\eta`\mu`\mu]
    \morphism(0,400)/=/<400,-400>[T`T;]
  \efig
  \end{mathpar}
\end{definition}

@@

  $$\eta:id_\cat{C}\rightarrow GF$$
  $$\mu=GF\varepsilon_A=\varepsilon_{GFA}:GFGF\rightarrow GF$$
  where $\eta$ is the unit and $\mu$ is the counit in the adjunction $F:\cat{C}\dashv\cat{L}:G$,
  and $(F,m)$ and $(G,n)$ are monoidal functors. \\

@@

  $$\q{A,B}=G\m{A,B}\circ\n{FA,FB}:TA\otimes TB\rightarrow T(A\otimes B)$$
  $$\q{I}=G\m{I}\circ\n{I'}:I\rightarrow TI$$

@@

  \item $T$ is a monoidal functor i.e. the folllowing diagrams commute:

@@

            \alpha_{TA,TB,TC}`id_{TA}\otimes\q{B,C}`\q{A,B}\otimes id_{TC}``
            \q{A,B\otimes C}`\q{A\otimes B,C}`T\alpha_{A,B,C}]

@@

            \lambda_{TA}`\q{I}\otimes id_{TA}`T\lambda_A`\q{I,A}]

@@

            \rho_{TA}`id_{TA}\otimes\q{I}`T\rho_A`\q{A,I}]

@@

        We write $GF$ instead of $T$ in the diagram chasings for clarity. \\
        By replacing $\q{}$ with its definition, the first diagram above commutes by the
        following diagram chasing, where the two hexagons commute because $G$ and $F$ are

@@

        The first square above commutes by the following diagram chasing, in which the top

@@

        Similarly, the second square above commutes by the following diagram chasing:

@@

  \item $\eta$ is a monoidal natural transformation, i.e. the following diagrams commute. In
        fact, since $\eta$ is the unit of the monoidal adjunction, $\eta$ is monoidal and thus
        the following two diagrams commute.

@@

            `\eta_A\otimes\eta_B`\eta_{A\otimes B}`\q{A,B}]

@@

          \Vtriangle/->`=`<-/<400,400>[I`TI`I;\eta_I``\q{I}]

@@

  \item $\mu$ is a monoidal natural transformation, i.e. the following diagrams commute. Since
        $\mu=\varepsilon_{GFA}$, $\mu$ is obviously also monoidal since $\varepsilon$ also is.
        Thus the following diagrams commute.

@@

            `\mu_A\otimes\mu_B`\mu_{A\otimes B}`\q{A,B}]
          \morphism(0,400)<800,0>[T^2A\otimes T^2B`T(TA\otimes TB);\q{TA,TB}]
          \morphism(800,400)<700,0>[T(TA\otimes TB)`T^2(A\otimes B);T\q{A,B}]

@@

          \square/->`<-`<-`<-/<400,400>[T^2I`TI`TI`I;\mu_I`T\q{I}`\q{I}`\q{I}]

@@

However, the monad $T$ we get from the SMCC-Lambek model is not symmetric because the following
diagram does not commute:
\begin{mathpar}
\bfig
  \hSquares/->`->`->``->`->`->/<400>[
    GFA\otimes GFB`GFB\otimes GFA`G(FB\otimes'FA)`G(FA\otimes'FB)`GF(A\otimes B)`GF(B\otimes A);
    \e{GFA,GFB}`\n{FB,FA}`\n{FA,FB}``G\m{B,A}`G\m{A,B}`GF\e{A,B}]
\efig
\end{mathpar}

Therefore, the monad is non-commutative.

>>>>

@@

@@

  $$\eta_A:A\rightarrow GFA$$
  $$\mu_A=G\varepsilon_{FA}:GFGFA\rightarrow GFA$$
  where $\eta$ is the unit and $\varepsilon:FG\rightarrow id_\cat{L}$ is the counit in the
  adjunction $F:\cat{C}\dashv\cat{L}:G$, and $(F,\m{})$ and $(G,\n{})$ are monoidal functors. \\

@@

  $$\t{A,B}=G\m{A,B}\circ\n{FA,FB}:TA\otimes TB\rightarrow T(A\otimes B)$$
  $$\t{I}=G\m{I}\circ\n{I'}:I\rightarrow TI$$

@@

  \item $T$ is a monoidal functor, i.e. the folllowing diagrams commute:

@@

            \alpha_{TA,TB,TC}`id_{TA}\otimes\t{B,C}`\t{A,B}\otimes id_{TC}``
            \t{A,B\otimes C}`\t{A\otimes B,C}`T\alpha_{A,B,C}]

@@

            \lambda_{TA}`\t{I}\otimes id_{TA}`T\lambda_A`\t{I,A}]

@@

            \rho_{TA}`id_{TA}\otimes\t{I}`T\rho_A`\t{A,I}]

@@

        We write $GF$ instead of $T$ in the proof for clarity. \\
        By replacing $\t{}$ with its definition, the first diagram above commutes by the
        following commutative diagram, where the two hexagons commute because $G$ and $F$ are

@@

        The first square above commutes by the following commutative diagrams, in which the top

@@

        Similarly, the second square above commutes by the following commutative diagram:

@@

  \item $\eta$ is a monoidal natural transformation. In fact, since $\eta$ is the unit of the
        monoidal adjunction, $\eta$ is monoidal and thus the following two diagrams commute.

@@

            `\eta_A\otimes\eta_B`\eta_{A\otimes B}`\t{A,B}]

@@

          \Vtriangle/->`=`<-/<400,400>[I`TI`I;\eta_I``\t{I}]

@@

  \item $\mu$ is a monoidal natural transformation. It is obvious that since
        $\mu=G\varepsilon_{FA}$ and $\varepsilon$ is monoidal, so is $\mu$. Thus the following
        diagrams commute.

@@

            `\mu_A\otimes\mu_B`\mu_{A\otimes B}`\t{A,B}]
          \morphism(0,400)<800,0>[T^2A\otimes T^2B`T(TA\otimes TB);\t{TA,TB}]
          \morphism(800,400)<700,0>[T(TA\otimes TB)`T^2(A\otimes B);T\t{A,B}]

@@

          \square/->`<-`<-`<-/<400,400>[T^2I`TI`TI`I;\mu_I`T\t{I}`\t{I}`\t{I}]

@@

However, the monad is not symmetric becauase the following diagram does not commute, for the
lambek category $\cat{L}$ is not symmetric.
\begin{mathpar}
\bfig
  \ptriangle/->`->`/<900,400>[
    GFA\otimes GFB`GFB\otimes GFA`G(FA\otimes'FB);\e{GFA,GFB}`\n{FA,FB}`]
  \morphism(900,400)<900,0>[GFB\otimes GFA`G(FB\otimes' FA);\n{FB,FA}]
  \dtriangle(900,0)/`->`->/<900,400>[
    G(FB\otimes'FA)`GF(A\otimes B)`GF(B\otimes A);`G\m{B,A}`GF\e{A,B}]
  \morphism|b|<900,0>[G(FA\otimes'FB)`GF(A\otimes B);G\m{A,B}]
\efig
\end{mathpar}
  \label{lem:strong-monad}
  The monad on the SMCC in a SMCC-Lambek model is strong.
  Let $F:\cat{C}\vdash\cat{L}:G$ be a SMCC-Lambek model, where
  $(\cat{C},\otimes,I,\alpha,\lambda,\rho)$ is an SMCC,
  $(\cat{L},\otimes',I',\alpha',\lambda',\rho')$ is a Lambek category, and $(F,\m{})$ and
  $(G,\n{})$ are monoidal functors. Let $(T,\eta,\mu)$ be the monad on $\cat{C}$ where
  $T=GF$. We have proved that $T$ is monoidal with the natural transformation
  $\t{A,B}:TA\otimes TB\rightarrow T(A\otimes B)$ and the morphism $\t{I}:I\rightarrow TI$
  defined as in Lemma~\ref{lem:monoidal-monad}. \\
  We define the tensorial strength $\tau_{A,B}:A\otimes TB\rightarrow T(A\otimes B)$ as
  $\tau_{A,B}=\t{A,B}\circ\eta_A\otimes id_{TB}$. \\
  Since $\eta$ is a monoidal natural transformation, we have $\eta_I=G\m{I}\circ\n{I'}$.
  Therefore $\eta_I=\t{I}$. Thus the following diagram commutes because $T$ is monoidal,
  where the composition $\t{I,A}\circ\t{I}\otimes id_{TA}$ is the definition of $\tau_{I,A}$. So
  the first triangle in Defition~\ref{def:strong-monad} commutes.
    \square/->`->`->`<-/<600,400>[
      I\otimes TA`TI\otimes TA`TA`T(I\otimes A);
      \t{I}\otimes id_{TA}`\lambda_{TA}`\t{I,A}`T\lambda_A]
  Similarly, by using the definition of $\tau$, the the second triangle in the definition is
  equivalent to the following diagram, which commutes because $\eta$ is a monoidal natural
  transformation:
    \square/->`->`->`<-/<600,400>[
      A\otimes B`A\otimes TB`T(A\otimes B)`TA\otimes TB;
      id_A\otimes\eta_B`\eta_{A\otimes B}`\eta_A\otimes id_{TB}`\t{A,B}]
    \morphism(0,400)|m|<600,-400>[A\otimes B`TA\otimes TB;\eta_A\otimes\eta_B]
  The first pentagon in the definition commutes by the following commutative diagrams, because
  $\eta$ are $\alpha$ natural transformations and $T$ is monoidal:
    \qtriangle|amm|/->`->`<-/<1000,400>[
      (A\otimes B)\otimes TC`T(A\otimes B)\otimes TC`(TA\otimes TB)\otimes TC;
      \eta_{A\otimes B}\otimes id_{TC}`
      (\eta_A\otimes\eta_B)\otimes id_{TC}`
      \t{A,B}\otimes id_{TC}]
    \morphism(0,400)<0,-400>[(A\otimes B)\otimes TC`A\otimes(B\otimes TC);\alpha_{A,B,TC}]
    \morphism(1000,0)|m|<0,-400>[
      (TA\otimes TB)\otimes TC`TA\otimes(TB\otimes TC);\alpha_{TA,TB,TC}]
    \Dtriangle(0,-800)|lmm|/->`->`<-/<1000,400>[
      A\otimes(B\otimes TC)`TA\otimes(TB\otimes TC)`A\otimes(TB\otimes TC);
      id_A\otimes(\eta_B\otimes id_{TC})`
      \eta_A\otimes(\eta_B\otimes id_{TC})`
      \eta_A\otimes id_{TB\otimes TC}]
    \morphism(0,-800)|b|<1000,0>[
      A\otimes(TB\otimes TC)`A\otimes T(B\otimes C);id_A\otimes\t{B,C}]
    \qtriangle(1000,0)|amr|/->``->/<1000,400>[
      \t{A\otimes B,C}``T\alpha_{A,B,C}]
    \morphism(2000,-800)<0,800>[
      TA\otimes T(B\otimes C)`T(A\otimes(B\otimes C));\t{A,B\otimes C}]
    \btriangle(1000,-800)|mmb|/`->`->/<1000,400>[
      TA\otimes(TB\otimes TC)`A\otimes T(B\otimes C)`TA\otimes T(B\otimes C);
      `id_{TA}\otimes\t{B,C}`\eta_A\otimes id_{T(B\otimes C)}]
  The last diagram in the definition commtues by the following commutative diagram, because
  $T$ is a monad, $\t{}$ is a natural transformation, and $\mu$ is a monoidal natural
  transformation:
    \ptriangle/->`->`/<700,400>[
      A\otimes T^2B`TA\otimes T^2B`A\otimes TB;\eta_A\otimes id_{T^2B}`id_A\otimes\mu_B`]
    \btriangle(0,-400)/->``->/<700,400>[
      A\otimes TB`TA\otimes TB`T(A\otimes B);\eta_A\otimes id_{TB}``\t{A,B}]
    \morphism(700,400)|m|<-700,-800>[TA\otimes T^2B`TA\otimes TB;id_{TA}\otimes\mu_B]
    \morphism(700,0)|m|<-700,-400>[TA\otimes T^2B`TA\otimes TB;id_{TA}\otimes\mu_B]
    \qtriangle(700,0)/->``->/<1800,400>[
      TA\otimes T^2B`T(A\otimes TB)`T(TA\otimes TB);\t{A,TB}``T(\eta_A\otimes id_{TB})]
    \btriangle(700,0)|mmm|/=`->`<-/<900,400>[
      TA\otimes T^2B`TA\otimes T^2B`T^2A\otimes T^2B;
      `T\eta_A\otimes id_{T^2B}`\mu_A\otimes id_{T^2B}]
    \morphism(1600,0)|m|<900,0>[T^2A\otimes T^2B`T(TA\otimes TB);\t{TA,TB}]
    \morphism(1600,0)|m|<-1600,-400>[T^2A\otimes T^2B`TA\otimes TB;\mu_A\otimes\mu_B]
    \dtriangle(700,-400)/`->`<-/<1800,400>[
      T(TA\otimes TB)`T(A\otimes B)`T^2(A\otimes B);`T\t{A,B}`\mu_{A\otimes B}]

\begin{lemma}[\cite{kock1970monads}]
  Let $\cat{M}$ be a symmetric monoidal category and $T$ be a strong monad on $\cat{M}$. Then
  $T$ is a symmetric monoidal functor iff it is commutative.
\end{lemma}

\begin{theorem}
  The monad on the SMCC in a SMCC-Lambek model is monoidal and non-commutative.
\end{theorem}

\begin{lemma}
  The comonad on the Lambek category in a SMCC-Lambek model is monoidal.
\end{lemma}
\begin{proof}
  We define the comonad $S$ on the Lambek category $\cat{L}$ in the adjunction
  $F:\cat{C}\vdash\cat{L}:G$ of a SMCC-Lambek model as $S=FG$, and the two corresponding natural
  transformations $\varepsilon:S\rightarrow id_\cat{L}$ and $\delta:S\rightarrow S^2$ are
  defined as
  $$\varepsilon_A:SA\rightarrow A$$
  $$\delta_A=F\eta_{GA}:SA\rightarrow S^2A$$
  where $\varepsilon$ is the counit and $\eta:id_\cat{L}\rightarrow GF$ is the unit in the
  adjunction, and $(F,\m{})$ and $(G,\n{})$ are monoidal functors. Thus, we have
  $$\s{A,B}=F\n{A,B}\circ\m{GA,GB}:SA\otimes'SB\rightarrow SA\otimes'SB$$
  $$\s{I}=F\n{I'}\circ\m{I}:I'\rightarrow SI'$$
  The comonad $S$ being monoidal means
  \begin{enumerate}
  \item $S$ is a monoidal functor, i.e. the following diagrams commute:
        \begin{mathpar}
        \bfig
          \hSquares/->`->`->``->`->`->/<400>[
            (SA\otimes'SB)\otimes'SC`SA\otimes'(SB\otimes'SC)`SA\otimes'S(B\otimes'C)`
            S(A\otimes'B)\otimes'SC`S((A\otimes'B)\otimes'C)`S(A\otimes'(B\otimes'C));
            \alpha_{SA,SB,SC}'`id_{SA}\otimes'\s{B,C}`\s{A,B}\otimes'id_{SC}``
            \s{A,B\otimes'C}`\s{A\otimes'B,C}`S\alpha_{A,B,C}']
        \efig
        \and
        \bfig
          \square/->`->`<-`->/<600,400>[
            I'\otimes'SA`SA`SI'\otimes'SA`S(I'\otimes'A);
            \lambda_{SA}'`\s{I'}\otimes'id_{SA}`S\lambda_A'`\s{I',A}]
        \efig
        \and
        \bfig
          \square/->`->`<-`->/<600,400>[
            SA\otimes'I'`SA`SA\otimes'SI'`S(A\otimes'I');
            \rho_{SA}'`id_{SA}'\otimes'\s{I'}`S\rho_A'`\s{A,I'}]
        \efig
        \end{mathpar}
  \item $\varepsilon$ is a monoidal natural transformation:
        \begin{mathpar}
        \bfig
          \square/->`->`->`=/<600,400>[
            SA\otimes'SB`S(A\otimes'B)`A\otimes'B`A\otimes'B;
            \s{A,B}`\varepsilon_A\otimes'\varepsilon_B`\varepsilon_{A\otimes'B}`]
        \efig
        \and
        \bfig
          \Vtriangle/->`<-`=/<400,400>[SI'`I'`I';\varepsilon_{I'}`\s{I'}`]
        \efig
        \end{mathpar}
  \item $\delta$ is a monoidal natural transformation:
        \begin{mathpar}
        \bfig
          \square/->`->`->`/<1500,400>[
            SA\otimes'SA`S(A\otimes'B)`S^2A\otimes'S^2B`S^2(A\otimes'B);
            \s{A,B}`\delta_A\otimes'\delta_B`\delta_{A\otimes'B}`]
          \morphism<800,0>[S^2A\otimes'S^2B`S(SA\otimes'SB);\s{SA,SB}]
          \morphism(800,0)<700,0>[S(SA\otimes'SB)`S^2(A\otimes'B);S\s{A,B}]
        \efig
        \and
        \bfig
          \square/->`<-`<-`->/<400,400>[
            SI'`S^2I'`I'`SI';\delta_{I'}`\s{I'}`S\s{I'}`\s{I'}]
        \efig
        \end{mathpar}
  \end{enumerate}
  The proof for the commutativity of the diagrams are similar as the proof in
  Lemma~\ref{lem:monoidal-monad}. We do not include the proof here for simplicity.
\end{proof}
